Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-14 aistats.tex
update section 6

Statistics typically give results on $\nat$, but the MAP~\eqref{eq:defMAP} is more simply expressed with $\meanp$, so let us focus on $\bregmanconj$.
Bregman divergences are locally quadratic, as seen via a second order Taylor expansion
\alignn{
    \bregmanconj(\m^* ; \m)
    &= \frac{\norm{\m^* - \m}^2_{\mF}}{2}
    + O(\norm{\m - \m^*}^3),
    \label{eq:bregmanTaylor}
}
where the Mahalanobis norm  $\| x \|_{\mF}^2 = x^\top \mF x$  is induced by $\mF  := \nabla^2\conj(\m^*)$, the hessian of the entropy at the optimum. It happens that  $\mF$ is also the inverse \textit{Fisher information matrix} at $\nat^*$, since
\aligns{
    \mF
    :=\nabla^2\conj(\m^*)
    = \nabla^2\logpart(\nat^*)^{-1}
    = \Cov_{\nat^*}[T(X)]^{-1}  \; .
}
Plugging the MLE~\eqref{eq:defMLE} or MAP~\eqref{eq:defMAP} into~\eqref{eq:bregmanTaylor}, one can show  that 
\begin{align}
	\label{eq:asymptote}
	\E \bregmanconj \left (\E [T(X)] ; \hat \meanp_n^\text{MLE/MAP} \right )
	= \frac{d}{2n} + O(n^{- \frac{3}{2}}) \; .
\end{align}
Both MLE and MAP have the same asymptote, as the contribution of the prior $n_0 \meanp_0$ gets negligible compared to the data for large $n$.
For well-specified models, this asymptote is also independent of the optimum $\meanp^*$. or $\mF$.
Let us see another example for which it is trivial to get a rate matching~\eqref{eq:asymptote}.

\subsection{Quadratic Case}
\label{ssec:quadratic}
As another classical reference point, let us consider the case $\logpart(\nat) = \half \norm{\nat}_2^2$.
For instance, this is the log-partition of a Gaussian with known variance $I$,
\[
	\cX=\real^d,\quad \nu(dx) = \exp\paren{\textstyle \half[-\|x\|^2]} dx,\quad T(x)=x.
\]
Then $\conj(\meanp) = \half \norm{\meanp}_2^2$ as well, and both Bregman divergences are squared $\ell^2$ distances:
\begin{align}
	\bregmanconj(\meanp^* ; \meanp) = \half \norm{\meanp^* -  \meanp }_2^2  \; .
\end{align}
Thanks to the independence of samples, we can break down the MLE into individual point's contributions
\begin{align}
	\expect{\half \norm{\m^* -  \inv{n}  \smallsum_i T_i}_2^2}
	=\frac{\Var(T)}{2n}
	=\frac{d}{2n}
\end{align}
Adding a reference mean $\m_0$ to get the MAP yields
\begin{align}
	\expect{\bregmanconj(\meanp^*; \MAPm)}
	&= \frac{n \Var(T) +  n_0^2 \norm{\m^* -  \m_0}^2}{2(n+n_0)^2}.
	%\\ &= O\left(\frac{\Var(T)}{n} \right) + O\left(\frac{\norm{\m^* -  \m_0}^2}{n^2} \right)
	\label{eq:MAP_quadratic}
\end{align}
So we see a variance term defining the $\frac{d}{2n}$ asymptote and a bias term in $O(n^{-2})$.
Can we generalize these results to other families ?
If we make restrictive assumptions on the log-partition function, we can relate $\bregmanconj$ to a norm or a quadratic.

{\bf If $\conj$ is $L$-Lipschitz} (e.g. $\logpart$ is defined within the $\ell^2$-ball of radius $L$), then
\begin{align}
    \bregmanconj(\m^* ; \m)
    &\leq L \norm{\m^* - \m} + \norm{\nat} \norm{\m^* - \m} \\
    &\leq 2L \norm{\m^* - \m}
\end{align}
so $\bregmanconj$ is $2L$-Lipschitz, and~\eqref{eq:MAP_quadratic} yields a $O(\inv{\sqrt{n}})$ rate.
However none of the common exponential families verify this assumption.

{\bf If $\conj$ is $L$-smooth}\footnote{$\conj$ is $L$-smooth iff $\nabla\conj$ is $L$-Lipschitz.} (e.g. $\logpart$ is $\frac{1}{L}$-strongly convex \citep{kakade2009duality}), then
\begin{align}
    \bregmanconj(\m^* ; \m)
    \leq \frac{L}{2} \norm{\m^* - \m}^2
\end{align}
so $\bregmanconj$ is upper bounded by a quadratic, and we get~\eqref{eq:MAP_quadratic} as an upper bound.
It is also possible to get (more complex) upper bounds under restricted notions of strong-convexity \citep{negahban2012unified}.
The problem is that, besides the Gaussian with known variance, no standard exponential family has a strongly convex log-partition function.
So let us focus on a more realistic set of assumptions in the next section.

\subsection{Locally Quadratic Case}
\label{ssec:local-quadratic}
From Taylor expansion~\eqref{eq:bregmanTaylor},
we know that all Bregman divergences are locally quadratic.
Under some assumptions, such as self-concordance\footnote{
In 1d, $f$ is self-concordant iff $\forall x, \abs{f'''(x)} \leq 2 \abs{f''(x)}^{\frac{3}{2}}$.
} of $\conj$ \citep[Ch.4.1]{nesterov2003introductory}, we can quantify when this quadratic behavior kicks in. Proofs for this subsection are in \cref{app:self-concordant}.
\begin{proposition}
Let $\conj:\cM\rightarrow \real$ be a self-concordant convex function, $\m, \m^* \in\cM$ and $\mF = \nabla \conj(\m^*)$. Then\footnote{$0.21$ is a value of $x$ such that $x^2 \geq -\frac{x}{1-x} - \log(1 - \frac{x}{1-x})$}.
\aligns{
	\norm{\m^*-\m}_{\mF} < 0.21
	\implies
	\bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF}^2
}
\end{proposition}
To gain insights into how many samples are needed, we can estimate when $\expecti{\norm{\m^*-\m}_{\mF}} < 0.21 $.
For the MLE, $\expecti{\norm{\m^*-\hat \m_n}_{\mF}} = \frac{d}{n}$, so a sufficient condition is $n \geq 5 d$.
For MAP, using~\eqref{eq:MAP_quadratic}, we get the sufficient condition $n\geq 5d + \sqrt{5}\norm{\m^* -  \m_0} - n_0$.
This means that on average, we need $5$ times more samples than the dimension to reach the quadratic regime where a formula like~\eqref{eq:MAP_quadratic} is valid.

@@

\subsection{Bias-Variance Decomposition}
\label{ssec:bias-variance}
In both the quadratic~\eqref{eq:MAP_quadratic} and the Gaussiance variance examples~\eqref{eq:MAP_rate}, the upper bound takes the form $O(\inv{n}) + O(\frac{\text{bias}}{n^2})$, 
giving us a flavor of what we would like as a general result for exponential families : a finite sample convergence rate, with a variance and a bias terms that reflect the important constants of the problem.
In fact, such a decomposition exists for any Bregman divergence.
Let $\tilde \theta_n := \expecti{\hat \theta_n}$ be the expectation of the MAP in primal space, and $\tilde \m_n = \nabla \logpart(\tilde \theta_n )$ be its corresponding mean parameter.
As described by \citet[Theorem 0.1]{pfau2013generalized}, the  expected Bregman decomposes into
\begin{equation}
	\expect{\bregmanconj(\m^* ; \hat \m_n)} = {\bregmanconj(\m^* ; \tilde \m_n)}
	+ {\expect{\bregmanconj(\tilde \m_n ; \MAPm)}}
	\label{eq:primal_pivot}
\end{equation}

\textbf{Remark:} In this decomposition, the primal expectation $\expect{\hat \theta_n}$ is taking the role of pivot / reference point. An estimator will be unbiased if its primal expectation is non-zero.
However, this is not true for the the gaussian variance MLE, where the bias decreases like ${\bregmanconj(\m^* ; \tilde \m_n)} \leq \frac{2}{n(n-2)}$.
A contrario, the MLE is unbiased wrt the dual parameter, but the decomposition there is not clean.

@@

As introduced in the technical background, MAP can be interpreted as stochastic mirror descent (SMD).
This means that we may obtain a convergence rate for MAP from an optimization analysis, 
and any insights gained from the MAP may inform further design and analysis of SMD.
We first review the assumptions of relative smoothness, useful to deal with non-smooth functions, 
before investigating 3 analysis of SMD with the MAP.
\rlp{mention that examples have so far been lacking for relative SMD.}

\subsection{Relative Smoothness}
Mirror descent (MD) \citep{nemirovski1983problem,beck2003mirror}, also known as
Bregman (proximal) gradient, relative gradient descent or NoLips,
%Nemirovski introduced the algorithm, and Beck established the connection with Bregman divergences, e.g. the argmin form.
and SMD \citep{nemirovski2009robust,ghadimi2012optimal}
are typically encountered in non-smooth (online) optimization,
under bounded (or Lipschitz) gradient assumption on the objective $f$
and strong convexity assumption on the potential $\logpart$
\citep[Th.4.2(MD) \& Th.6.3(SMD)]{bubeck2015convex}.
In our case, these assumptions do not hold.
For instance $\logpart = -\log$ is neither smooth nor strongly convex.

Recently, these assumptions have been relaxed to the $\stgcvx$-strong convexity and $\smooth$-smoothness of $f$
\emph{relative} to a reference function $\logpart$, defined as
\aligns{
	\stgcvx \cB_{A}(x, y)
	\leq
	\cB_f(x,y)
	\leq
	\smooth \cB_A(x,y) \; .
}
When $\logpart = \norm{\cdot}^2$, we recover standard (Euclidean) smoothness, and gradient descent.
Those conditions ensure the linear convergence of MD with mirror map $\nabla A$,
extending the theory to non-smooth functions $f$ and non-strongly convex potential $\logpart$
\citep{birnbaum2011distributed, bauschke2017descent, lu2018relatively}.

For exponential families, the log-likelihood perfectly fit into this framework, as
\aligns{
	f(\theta) = A(\theta) - \expect{\lin{T(X), \theta}}
}
is both $1$-smooth and $1$-strongly convex relative to $A$. 
So we are left with finding an applicable convergence rate for SMD under relative assumptions.
As we investigate in the next section, several pieces of work have addressed this question, under various assumptions on the stochasticity \citep{hanzely2018fastest, dragomir2021fast, dorazio2021stochastic}.

@@

\textbf{Caveat:} these rates apply to the Bregman in the other direction, e.g. $\bregman(\nat^*, \MAPt)$, and sometimes not on the last iterate, but with tail averaging in the primal.

@@

\subsubsection{Bounded Variance}
\citet{hanzely2018fastest} assume the covariance between negative gradient and next iterate is upper bounded at every time step: $\forall n \geq 1, \forall \hat \nat_{n-1},$
\alignn{
	\Cov(-g_n(\hat \nat_{n-1}) , \MAPt) \leq \lr_n C
	\label{eq:hanzely}
}
for some constant $C$.
For a Gaussian with known variance ($A(\theta) = \frac{1}{2}\norm{\theta}^2$),
this definition recovers the variance of the stochastic gradient
\[
	\expect[\tilde g_t\!\!]{\norm{\nabla f(\theta) - \tilde g(\theta)}{}^2}\leq C.
\]
More generally, if $A$ is $\stgcvx$-strongly convex w.r.t. $\norm{\cdot}$,
the LHS of \cref{eq:hanzely} is bounded by
$\expecti{\frac{1}{\stgcvx}\norm{\nabla f(\theta) - \tilde g(\theta)}{}^2_*}$.
Then a bound on the variance of stochastic gradients is sufficient for \cref{eq:hanzely}
to hold.
%Another perspective on this covariance is as the expectation of the symmetrized Bregman $\cS_\conj(\m_1, \m_2) = \bregmanconj(\m_1, \m_2) + \bregmanconj(\m_2, \m_1)$ between stochastic and deterministic updates
%\aligns{
%\Cov(-g_n(\hat \nat_{n-1}) , \MAPt) = \E[\cS(\MAPm - \lr g_n  )]
%}
%thus showing positivity.
Under this assumption, \citet[Lem.4.8]{hanzely2018fastest} prove a $O(1/n)$ convergence rate with $O(1/n)$ step-sizes, 
by applying tail averaging \citep{lacostejulien2012simpler} in primal space $\Theta$.
But in general, this assumption rarely holds.
For the MAP, this translates into $\forall n \geq 1,$
\alignn{
\expect[T_n]{\lin{T_n - \mu^* , \MAPt}} \leq \lr_n C
}
which fails to hold on the gaussian variance example for instance. \TODO{ DAMIEN short proof or formalize.}

>>>>

Statistics typically give results on $\nat$, but the MAP~\eqref{eq:defMAP} is more simply expressed with $\meanp$, so let us focus on $\bregmanconj$.
Bregman divergences are locally quadratic, as seen via a second order Taylor expansion
\alignn{
    \textstyle \bregmanconj(\m^* ; \m)
    &\textstyle = \frac{1}{2}\norm{\m^* - \m}^2_{\mF}
    + O(\norm{\m - \m^*}^3),
    \label{eq:bregmanTaylor}
}
where the Mahalanobis norm  $\| x \|_{\mF}^2 = x^\top \mF x$  is induced by $\mF  := \nabla^2\conj(\m^*)$, the hessian of the entropy at the optimum. It happens that  $\mF$ is also the inverse \textit{Fisher information matrix} at $\nat^*$, since
\aligns{
    \mF
    :=\nabla^2\conj(\m^*)
    = \nabla^2\logpart(\nat^*)^{-1}
    = \Cov_{\nat^*}[T(X)]^{-1}  \; .
}
Plugging the MLE~\eqref{eq:defMLE} or MAP~\eqref{eq:defMAP} into~\eqref{eq:bregmanTaylor}, we have
\begin{align}
	\label{eq:asymptote}
	\E \bregmanconj \left (\E [T(X)] ; \hat \meanp_n^\text{MLE/MAP} \right )
	= \frac{d}{2n} + O(n^{- \frac{3}{2}}) \; .
\end{align}
Both MLE and MAP have the same asymptote, as the contribution of the prior $n_0 \meanp_0$ gets negligible for large $n$.
For well-specified models, this asymptote is also independent of the optimum $\meanp^*$ or $\mF$.
Let us see another example for which we get a rate matching~\eqref{eq:asymptote}.

\subsection{Quadratic Case}
\label{ssec:quadratic}
As another classical reference point, we consider the case $\logpart(\nat) = \half \norm{\nat}_2^2$.
For instance, this is the log-partition of a Gaussian with known variance $I$,
\[
	\cX=\real^d,\quad \nu(dx) = \exp\paren{\textstyle \half[-\|x\|^2]} dx,\quad T(x)=x.
\]
In this case, $\conj(\meanp) = \half \norm{\meanp}_2^2$ as well, and both Bregman divergences are squared $\ell^2$ distances since
\begin{align}
	\bregmanconj(\meanp^* ; \meanp) = \half \norm{\meanp^* -  \meanp }_2^2  \; .
\end{align}
Thanks to the independence of samples, we can break down the MLE into individual point's contributions:
\begin{align}
	\expect{\half \norm{\m^* -  \inv{n}  \smallsum_i T_i}_2^2}
	=\frac{\Var(T)}{2n}
	=\frac{d}{2n}.
\end{align}
Adding a reference mean $\m_0$ to get the MAP yields
\begin{align}
	\expect{\bregmanconj(\meanp^*; \MAPm)}
	&= \frac{n \Var(T) +  n_0^2 \norm{\m^* -  \m_0}^2}{2(n+n_0)^2}.
	%\\ &= O\left(\frac{\Var(T)}{n} \right) + O\left(\frac{\norm{\m^* -  \m_0}^2}{n^2} \right)
	\label{eq:MAP_quadratic}
\end{align}
We see here a variance term defining the $\frac{d}{2n}$ asymptote and a bias term in $O(n^{-2})$. However, this result does not generalize well to other families, unless we make restrictive assumptions on $\conj$. % we can relate $\bregmanconj$ to a norm or a quadratic.
% Can we generalize these results to other families?

{\bf If $\conj$ is $L$-Lipschitz} (e.g. $\logpart$ is defined within the $\ell^2$-ball of radius $L$), then
\begin{align}
    \bregmanconj(\m^* ; \m)
    &\leq L \norm{\m^* - \m} + \norm{\nat} \norm{\m^* - \m} \\
    &\leq 2L \norm{\m^* - \m},
\end{align}
so $\bregmanconj$ is $2L$-Lipschitz, and~\eqref{eq:MAP_quadratic} yields a $O(\inv{\sqrt{n}})$ rate.
However none of the common exponential families verify this assumption.

{\bf If $\conj$ is $L$-smooth}\footnote{$\conj$ is $L$-smooth iff $\nabla\conj$ is $L$-Lipschitz.} (e.g. $\logpart$ is $\frac{1}{L}$-strongly convex \citep{kakade2009duality}), then
\begin{align}
    \bregmanconj(\m^* ; \m)
    \leq \frac{L}{2} \norm{\m^* - \m}^2,
\end{align}
so $\bregmanconj$ is upper bounded by a quadratic, and we get~\eqref{eq:MAP_quadratic} as an upper bound.
It is also possible to get (more complex) upper bounds under restricted notions of strong-convexity \citep{negahban2012unified}.
The problem is that, besides the Gaussian with known variance, no standard exponential family has a \textit{global} strongly convex log-partition function. The next section focuses on \textit{local} quadratic behavior, which is more realistic.
% So let us focus on a more realistic set of assumptions in the next section.

\subsection{Locally Quadratic Case}
\label{ssec:local-quadratic}
From Taylor expansion~\eqref{eq:bregmanTaylor},
we know that all Bregman divergences are locally quadratic.
Under some assumptions, such as self-concordance\footnote{
In 1d, $f$ is self-concordant iff $\forall x, \abs{f'''(x)} \leq 2 \abs{f''(x)}^{\frac{3}{2}}$.
} of $\conj$ \citep[Ch.4.1]{nesterov2003introductory}, we can quantify when this quadratic behavior kicks in. Proofs for this subsection are in \cref{app:self-concordant}.
\begin{proposition}
Let $\conj:\cM\rightarrow \real$ be a self-concordant convex function, $\m, \m^* \in\cM$ and $\mF = \nabla \conj(\m^*)$. Then\footnote{$0.21$ is a value of $x$ such that $x^2 \geq -\frac{x}{1-x} - \log(1 - \frac{x}{1-x})$}
\aligns{
	\norm{\m^*-\m}_{\mF} < 0.21
	\implies
	\bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF}^2.
}
\end{proposition}
To gain insights into how many samples are needed, we can estimate when $\expecti{\norm{\m^*-\m}_{\mF}} < 0.21 $.
For the MLE, $\expecti{\norm{\m^*-\hat \m_n}_{\mF}} = \frac{d}{n}$, so a sufficient condition is $n \geq 5 d$.
For MAP, using~\eqref{eq:MAP_quadratic}, we get the sufficient condition $n\geq 5d + \sqrt{5}\norm{\m^* -  \m_0} - n_0$.
This means that on average, we need $5$ times more samples than the dimension to reach the quadratic regime where a formula like~\eqref{eq:MAP_quadratic} is valid.

@@

\subsection{Bias-Variance Decomposition}
\label{ssec:bias-variance}
In both the quadratic~\eqref{eq:MAP_quadratic} and the Gaussiance variance examples~\eqref{eq:MAP_rate}, the upper bound takes the form $O(\inv{n}) + O(\frac{\text{bias}}{n^2})$, 
giving us a flavor of what we would like as a general result for exponential families: a finite sample convergence rate, with a variance and a bias terms that reflect the important constants of the problem.
In fact, such a decomposition exists for any Bregman divergence.
Let $\tilde \theta_n := \expecti{\hat \theta_n}$ be the expectation of the MAP in primal space, and $\tilde \m_n = \nabla \logpart(\tilde \theta_n )$ be its corresponding mean parameter.
As described by \citet[Theorem 0.1]{pfau2013generalized}, the  expected Bregman decomposes into
\begin{equation}
	\expect{\bregmanconj(\m^* ; \hat \m_n)} = {\bregmanconj(\m^* ; \tilde \m_n)}
	+ {\expect{\bregmanconj(\tilde \m_n ; \MAPm)}}
	\label{eq:primal_pivot}
\end{equation}

\textbf{Remark:} In this decomposition, the primal expectation $\expect{\hat \theta_n}$ is taking the role of pivot / reference point. An estimator will be unbiased if its primal expectation is non-zero.
However, this is not true for the the gaussian variance MLE, where the bias decreases like ${\bregmanconj(\m^* ; \tilde \m_n)} \leq \frac{2}{n(n-2)}$.
A contrario, the MLE is unbiased w.r.t. the dual parameter, but the decomposition there is not clean.

@@

As we saw in the technical background, MAP can be interpreted as stochastic mirror descent (SMD).
This means that \textbf{1)} we may obtain a convergence rate for MAP from an optimization analysis, and \textbf{2)} any insights gained from the MAP may inform further design and analysis of SMD.
We first review the assumptions of relative smoothness, useful to deal with non-smooth functions, before investigating three analyses of SMD with the MAP.
\rlp{mention that examples have so far been lacking for relative SMD.}

\subsection{Relative Smoothness}
Mirror descent (MD) \citep{nemirovski1983problem,beck2003mirror}, also known as
Bregman (proximal) gradient, relative gradient descent or NoLips,
%Nemirovski introduced the algorithm, and Beck established the connection with Bregman divergences, e.g. the argmin form.
and SMD
\citep{nemirovski2009robust,ghadimi2012optimal}
are typically encountered in non-smooth (online) optimization,
under bounded (or Lipschitz) gradient assumption on the objective $f$
and strong convexity assumption on the potential $\logpart$
\citep[Th.4.2(MD) \& Th.6.3(SMD)]{bubeck2015convex}.
In our case, none of these assumptions may hold.
For instance $\logpart = -\log$ is neither smooth nor strongly convex.

Recent works extend these assumptions to the $\stgcvx$-strong convexity and $\smooth$-smoothness of $f$
\emph{relative} to $\logpart$,
\aligns{
	\stgcvx \cB_{A}(x, y)
	\leq
	\cB_f(x,y)
	\leq
	\smooth \cB_A(x,y) \; .
}
When $\logpart = \norm{\cdot}^2$, we recover standard (Euclidean) smoothness, and gradient descent.
Those conditions ensure the linear convergence of MD with $A$ as the reference function,
thus extending the theory to a family of non-smooth functions $f$ and non-strongly convex potential $\logpart$
\citep{birnbaum2011distributed, bauschke2017descent, lu2018relatively}.

For exponential families, the log-likelihood perfectly fit into this framework, as
\aligns{
	f(\theta) = A(\theta) - \expect{\lin{X, \theta}}
}
is both $1$-smooth and $1$-strongly convex relative to $A$. 
So we are left with finding an applicable convergence rate for SMD under relative assumptions.
As we investigate in the next section, several pieces of work have addressed this question, under various assumptions on the stochasticity \citep{hanzely2018fastest, dragomir2021fast, dorazio2021stochastic}.

@@

\textbf{Caveat :} all of these rates apply to the Bregman in the other direction, e.g. $\bregman(\nat^*, \MAPt)$, and sometimes not on the last iterate, but with tail averaging.

@@

\subsubsection{Bounded Variance}
\citet{hanzely2018fastest} assume the covariance between negative gradient and next iterate is upper bounded at every time step: $\forall n \geq 1, \forall \hat \nat_{n-1},$
\alignn{
\Cov(-g_n(\hat \nat_{n-1}) , \MAPt) \leq \lr_n C
\label{eq:hanzely}
}
for some constant $C$.
For a Gaussian with known variance ($A(\theta) = \frac{1}{2}\norm{\theta}^2$),
this definition recovers the variance of the stochastic gradient
\[
	\expect[\tilde g_t\!\!]{\norm{\nabla f(\theta) - \tilde g(\theta)}{}^2}\leq C.
\]
More generally, if $A$ is $\stgcvx$-strongly convex w.r.t. $\norm{\cdot}$,
the LHS of \cref{eq:hanzely} is bounded by
$\expecti{\frac{1}{\stgcvx}\norm{\nabla f(\theta) - \tilde g(\theta)}{}^2_*}$.
Then a bound on the variance of stochastic gradients is sufficient for \cref{eq:hanzely}
to hold.
%Another perspective on this covariance is as the expectation of the symmetrized Bregman $\cS_\conj(\m_1, \m_2) = \bregmanconj(\m_1, \m_2) + \bregmanconj(\m_2, \m_1)$ between stochastic and deterministic updates
%\aligns{
%\Cov(-g_n(\hat \nat_{n-1}) , \MAPt) = \E[\cS(\MAPm - \lr g_n  )]
%}
%thus showing positivity.
Under this assumption, \citet[Lem.4.8]{hanzely2018fastest} prove a $O(1/n)$ convergence rate with a $O(1/n)$ step-size, by applying polynomial tail averaging \citep{lacostejulien2012simpler} in primal space $\Theta$.

In general however, this assumption hardly holds.
For the MAP, this translates into $\forall n \geq 1,$
\alignn{
\expect[T_n]{\lin{T_n - \meanp^* , \MAPt}} \leq \lr_n C
}
which fails to hold on the gaussian variance example for instance. Indeed, we cannot control the samples $x_i$, therefore there is a non-zero probability they make $\nabla\conj(\MAPt) = \hat\meanp_t$ arbitrarily close to zero. Since the conjugate of the log partition is $\conj=-0.5\log$, this makes $\MAPt$ unbounded.

%  \TODO{ DAMIEN short proof or formalize.}
